\documentclass{article}
\renewcommand\familydefault{\sfdefault}
\usepackage[margin=1.75in]{geometry}
\setlength{\parindent}{0ex}
\setlength{\parskip}{0.5ex}
\usepackage{xcolor}
\usepackage{natbib}
%\bibliographystyle{apj}

\usepackage{titlesec}
%\setcounter{secnumdepth}{0}
\titlespacing*{\section}{-0.5in}{0ex}{0ex}
\titlespacing*{\subsection}{-0.25in}{0ex}{0ex}

\usepackage{enumitem}
%\setlist[itemize]{%
\setitemize{%
    label={\footnotesize$\bullet$}
}
\setdescription{%
    style=nextline,
    %itemindent=0em,
    leftmargin=1em, % text describing the source, outside the label
    }
\renewcommand{\descriptionlabel}{%
    \bfseries}

\usepackage{hyperref}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\hypersetup{colorlinks=true, urlcolor=cobalt, linkcolor=black}
\urlstyle{same}

\begin{document}
\section{Papers}

\subsection{Coronal bright points}
\begin{description}
    \item [\href{http://adsabs.harvard.edu/abs/2015ApJ...807..175A}
        {Statistical properties of solar coronal bright points}\\
        -Alipour \& Safari]
	\item [\href{http://cdsads.u-strasbg.fr/abs/2009MNRAS.397.1852C}
        {Automated detection and tracking of solar magnetic bright points}\\
        -Crockett, Jess, Mathioudakis, and Keenan (2009)]
    \item [%\href{https://arxiv.org/abs/1208.4693}
        {Title(s) here}\\
        -Golub et al. 1976 (2 papers)]
	\item [\href{http://cdsads.u-strasbg.fr/abs/2011A\%26A...526A..78K}
        {Temperature variability in X-ray bright points observed with Hinode/XRT}\\
        -Kariyappa et al. 2011]
        Temperature and density of coronal bright points.
    \item [\href{http://cdsads.u-strasbg.fr/abs/2007ApJ...670.1401M}
        {On the Mass and Energy Loading of Extreme-UV Bright Points}\\
        -McIntosh, S. W.]
        CBPs are actually loops?
	\item [\href{http://cdsads.u-strasbg.fr/abs/1994ApJ...427..459P}
        {A converging flux model of an X-ray bright point and an associated canceling magnetic feature}\\
        -Priest, Parnell, \& Martin (1994)]
	\item [\href{http://cdsads.u-strasbg.fr/abs/2015ApJ...806..172S}
        {Quasi-periodic oscillation of a coronal bright point}\\
        -Samanta, Banerjee, and Tian (2015)]
	\item [%\href{}
        {Title here}\\
        -Vaiana et al. 1973]
        Discoverer of coronal bright points.
	\item [\href{http://cdsads.u-strasbg.fr/abs/2012ApJ...753...35V}
        {Evidence for widespread cooling in an active region observed with the
        \textit{SDO} Atmospheric Imaging Assembly}\\
        -Viall and Klimchuk 2012]
	\item [\href{}
        {The correspondence between X-ray bright points and evolving magnetic features
        in the quiet sun}\\
        -Webb, Martin, Moses, \& Harvey (1993)]
	\item [\href{http://ads.nao.ac.jp/abs/2014A\%26A...568A..30Z}
        {Reciprocatory magnetic reconnection in a coronal bright point}\\
        -Zhang et al. (2014)]
        CBP complex, two patches, flux normalized by background
	\item [\href{http://cdsads.u-strasbg.fr/abs/2012ApJ...746...19Z}
        {Two types of magnetic reconnection in coronal bright points and the
        corresponding magnetic configuration}\\
        -Zhang et al. (2012)]
        Rotation $\rightarrow$ merging $\rightarrow$ jet! Threshold for BP defined
        as greater than 3 sigma level of background.
\end{description}


\subsection{Alfv\'en waves}
\begin{description}
    \item [\href{http://arxiv.org/abs/0903.3546}
        {Alfv\'en waves in the lower solar atmosphere}\\
        - Jess, 2009]
    \item [\href{https://arxiv.org/abs/0910.0962}
        {The role of torsional Alfv\'en waves in coronal heating}\\
        - P. Antolin, K. Shibata]
\end{description}

\subsection{Instrumentation}
\begin{description}
    \item [\href{http://cdsads.u-strasbg.fr/abs/2012SoPh..275...17L}
            {The (AIA) on (SDO)}]
            Obviously$\ldots$ AIA info.
\end{description}

\subsection{Coronal seismology}
\begin{description}
    \item [\href{http://link.springer.com/article/10.1007\%2Fs11207-007-9029-z}
        {Present and Future Observing Trends in Atmospheric Magnetoseismology}]
    \item [\href{http://arxiv.org/abs/1304.5439}
        {Modeling the Line-of-Sight Integrated Emission in the Corona:
        Implications for Coronal Heating}
        - Viall and Klimchuk]
    \item [\href{http://rsta.royalsocietypublishing.org/content/370/1970/3193}
        {Magnetohydrodynamic waves and coronal seismology: an overview of recent results}]
        - Ineke De Moortel, Valery M. Nakariakov
    \item [\href{http://arxiv.org/abs/1509.05519}
        {Decayless low-amplitude kink oscillations: a common phenomenon in the solar corona?}]
    \item [\href{http://adsabs.harvard.edu/abs/2016A\%26A...585L...6P}
        {Damping profile of standing kink oscillations observed by SDO/AIA}]
    \item [\href{http://cdsads.u-strasbg.fr/abs/2015arXiv151002750W}
        {Evidence of thermal conduction suppression in hot coronal loops:
            Supplementary results}\\
        -Wang, Ofman, Sun, Provornikova, and Davila]
        Paper from SPD meeting in Boulder
	\item [\href{http://cdsads.u-strasbg.fr/abs/2015ApJ...811L..13W`}
        {Evidence of Thermal Conduction Suppression in a Solar Flaring
            Loop by Coronal Seismology of Slow-mode Waves}\\
        -Wang, Ofman, Sun, Provornikova, and Davila]
        Another paper from SPD meeting in Boulder
\end{description}

\subsection{Granular structure}
\begin{description}
    \item [\href{http://cdsads.u-strasbg.fr/abs/1997ApJ...481..988H}
        {The distribution of cell sizes of the Solar Chromospheric Network}]
        from Priest, page 22, ``basin-finding'' algorithm for finding
        supergranules.
    \item [\href{http://cdsads.u-strasbg.fr/abs/2008A\%26A...479L..17R}
        {Solar supergranulation revealed by granule tracking}]
        Priest, page 22, granule tracking.
    \item [\href{http://cdsads.u-strasbg.fr/abs/1989ApJ...336..475T}
        {Statistical properties of solar granulation derived
        from the SOUP instrument on Spacelab 2}]
        Cited by Priest, having something to do with the motions of granules and supergranules.
    \item [\href{http://cdsads.u-strasbg.fr/abs/2000SoPh..193..313S}
        {Supergranule and mesogranule evolution}]
        Cited by Priest, along with November when
        discussing the difficulties of observing mesogranulation.
    \item [\href{http://adsabs.harvard.edu/cgi-bin/bib_query?arXiv:0902.2299}
        {Mesoscale dynamics on the Sun's surface from HINODE
        observations}]
    \item [\href{http://adsabs.harvard.edu/abs/1981ApJ...245L.123N}
        {The detection of mesogranulation on the sun}]
        the first to detect structure between granule
        and supergranule size scales.
\end{description}

\subsection{To be sorted}
\begin{description}
    \item [\href{http://adsabs.harvard.edu/abs/2004ApJ...613L.185F}
            {Helioseismic Mapping of the Magnetic Canopy in the Solar Chromosphere}\\
        -Finsterle, Jefferies, and McIntosh]
        Paper from first semester.
    \item [\href{http://cdsads.u-strasbg.fr/abs/2007AN....328..211H}
        {On the observation of traveling acoustic waves in the solar
            atmosphere using a magneto-optical filter}\\
        -Haberreiter, Finsterle, and Jefferies]
        Another paper from first semester.
	\item [\href{http://cdsads.u-strasbg.fr/abs/2012ApJ...749...40S}
        {Coronal Cells}\\
        -Sheeley and Warren]
	\item [\href{http://cdsads.u-strasbg.fr/abs/2013ApJ...772...88S}
        {Using Coronal Cells to Infer the Magnetic Field Structure and
            Chirality of Filament Channels}\\
        -Sheeley, Martin, Panasenco, and Warren]
    \item [\href{https://arxiv.org/abs/1208.4693}
        {Solar Force-free magnetic fields}\\
        - Thomas Weigelmann]
    \item [\href{http://cdsads.u-strasbg.fr/abs/1964ApJ...140.1120S}
        {Velocity fields in the solar atmosphere. III.
        Large-Scale Motions, the Chromospheric Network, and Magnetic Fields}\\
        - Priest]
        page 22, autocorrelation method for finding mean size of supergranules.
    \item [\href{https://arxiv.org/abs/1208.4693}
        {Solar Force-free magnetic fields}\\
        - Thomas Weigelmann]
\end{description}
\section{Other links}
\begin{itemize}
    \item \url{http://solarphysics.livingreviews.org/open?pubNo=lrsp-2010-2&amp;page=articlesu5.html}
    \item \url{http://solarphysics.livingreviews.org/Articles/lrsp-2012-5/download/lrsp-2012-5Color.pdf}
    \item \url{http://dkist.nso.edu}
\end{itemize}

%\bibliography{reffile}
%\end{flushleft}
\end{document}
